---
title: "rprojroot makes setwd() for Rmarkdown project so easy"
author: "Shengguo"
date: "`r Sys.time()`"
categories: ["R"]
tags: ["R Markdown", "rprojroot"]
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = FALSE,
	warning = FALSE,
	collapse = TRUE
)


# You can also embed plots. See Figure \@ref(fig:pie) for example:
```

Recently, just found that the package `rprojroot` is very useful when working on a Rmarkdown file. [See detail](https://rprojroot.r-lib.org/index.html). It makes `setwd()` for Rmarkdown project so much easier by simply adding this line of code into your first code chunk. 

`knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())`

__Inside a Rmarkdown project__

```{r echo=TRUE}
# To find the root directory for the root the project when using RStudio.
rprojroot::find_rstudio_root_file()  

# To check if a sub-directory exists
rprojroot::has_dir("data")

# To check if a file exists
rprojroot::has_file("index.md")
```

Similarly, it works for package project, `rprojroot::find_package_root_file()`.